---
title: "MetabFrench2019"
author: "Jacob Adams"
date: "10/17/2022"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

---

```{r knitr_init, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(width=80)
```

```{r libs, warning=FALSE, message=FALSE}
library(ggpubr)
library(anytime)
library(googlesheets4)
library(ggpmisc)
library(plyr)
library(dplyr)
library(lubridate)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(scales)
library(zoo)
library(xts)
library(forecast)
library(googledrive)
library(streamMetabolizer)
library(readr)
library(here)
library(rstan)
library(imputeTS)
library(itsmr)
library(purrr)
```

# 1. Preparing the input data and time frame
```{r data}
setwd(here())
FRCH.comb.in <- read.csv(here("outputs", "frch.comb.csv"))

FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-06-27 14:15:00", NA, .)))

FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-07-19 10:15:00", NA, .)))

FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-07-26 13:45:00", NA, .)))

FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-07-26 14:00:00", NA, .)))


FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-06-13 14:00:00", NA, .)))


FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-06-13 13:45:00", NA, .)))



FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-06-13 14:00:00", NA, .)))


FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-07-12 09:45:00", NA, .)))


FRCH.comb.in <- FRCH.comb.in %>%
  mutate(across(c(temp.water, ODO.Psat, ODO.Ploc, DO.obs, DO.sat.EXO, DO.sat),
                ~ifelse(datetimeAK == "2019-09-26 13:00:00", NA, .)))

#NA FILL OUT OF WATER and Other small gaps
FRCH.comb.in$temp.water <- na_kalman(FRCH.comb.in$temp.water)
FRCH.comb.in$ODO.Psat <- na_kalman(FRCH.comb.in$ODO.Psat)
FRCH.comb.in$DO.obs <- na_kalman(FRCH.comb.in$DO.obs, type = "level")
FRCH.comb.in$DO.sat <- na_kalman(FRCH.comb.in$DO.sat, type = "level")
FRCH.comb.in$DO.sat.EXO <- na_kalman(FRCH.comb.in$DO.sat.EXO, type = "level")
FRCH.comb.in$depth <- na_kalman(FRCH.comb.in$depth)
FRCH.comb.in$discharge <- na_kalman(FRCH.comb.in$discharge)



#Set time of run
FRCH.comb <- FRCH.comb.in %>% filter(solar.time >= "2019-03-15 04:13:57" & solar.time < "2019-11-30 13:45:00")



anyNA(FRCH.comb, recursive = TRUE)
lapply(FRCH.comb, summary)


FRCH.comb$datetimeAK <- force_tz(as.POSIXct(FRCH.comb$datetimeAK), "America/Anchorage")

FRCH.comb$solar.time <- calc_solar_time(as.POSIXct(FRCH.comb$datetimeAK), longitude = -146.916364)


#DO sat is DO sat EXO, duplicate cols
data.frch.mm <- FRCH.comb %>%
  select(solar.time, depth, DO.obs, DO.sat, temp.water, light, discharge)

anyNA(data.frch.mm, recursive = TRUE)
lapply(data.frch.mm, summary)

```

# 2. Configuring the model


```{r bayes_name}

bayes_name <- mm_name(type='bayes', pool_K600='binned', err_obs_iid=TRUE, err_proc_iid=TRUE)
bayes_name

bayes_name_AppEtAL <- "b_Kb_oipi_tr_plrckm.stan"
bayes_name_AppEtAL

```

## 2b. Set the specifications

We now pass the model name to `specs()` to get a
list of default specifications for this model.
```{r bayes_specs}
bayes_specs <- specs(bayes_name, 
                     burnin_steps=9000, saved_steps=5000, n_cores=8, n_chains = 4 
                     # GPP_daily_lower = 0, ER_daily_upper = 0
)
```


# 3. Fitting the model

```{r bayes_fit, cache=TRUE}
startTime <- as.POSIXct(Sys.time())
mm.test.frch <- metab(bayes_specs, data=data.frch.mm)
endTime <- as.POSIXct(Sys.time())

difftime(endTime, startTime)
save(mm.test.frch, file = here("Outputs", "aug28_oct10.RData"))


```



# 4. Inspecting the model

```{r}
fit.frch <- get_fit(mm.test.frch)
fit.daily <- fit.frch$daily
# 2019-06-15 04:13:57" & solar.time < "2019-07-29 04:13:57
write.csv(fit.daily, here("outputs", "aug28_oct10_full.csv"))

fit.daily.short <- fit.daily %>% select(GPP_daily_mean, ER_daily_mean, K600_daily_mean, GPP_daily_Rhat, ER_daily_Rhat, K600_daily_Rhat, valid_day,	warnings,	errors) 

write.csv(fit.daily.short, here("outputs", "aug28_oct10_short.csv"))

mm.test.frch

fit.frch
```


```{r, fig.width=10, fig.height=5}


gpp <- ggplot(data=fit.frch$daily, aes(x=date, y=GPP_mean)) + geom_point(color = "chartreuse4") + geom_errorbar(aes(ymin=GPP_mean-GPP_sd, ymax=GPP_mean+GPP_sd), width=.2, position=position_dodge(0.05), color = "chartreuse4") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.x=element_blank() )

```

```{r, fig.width=10, fig.height=5}
er <- ggplot(data = fit.daily, aes(x = date)) +geom_point(aes(y = ER_mean), color = "firebrick3") + geom_errorbar(aes(ymin=ER_mean-ER_sd, ymax=ER_mean+ER_sd), width=.2, position=position_dodge(0.05), color = "firebrick3") + ylim(-60, 10)

```

```{r , fig.width=10, fig.height=5}
rhat <- ggplot(data=fit.frch$daily, aes(x=date)) + geom_point(aes(y=GPP_Rhat, colour = "GPP")) + geom_point(aes(y=as.numeric(ER_Rhat), colour = "ER")) + geom_point(aes(y=K600_daily_Rhat, colour = "K600")) +
  labs(y = "RHAT") + theme(legend.position="top") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.x=element_blank() )

```

```{r, fig.width=10, fig.height=5}
ggplot(data=fit.daily, aes(x=GPP_mean, y=ER_mean)) + geom_point()+ stat_poly_line() + stat_poly_eq() 
```

```{r, fig.width=10, fig.height=5}
ggplot(data=fit.daily, aes(x=GPP_mean, y=K600_daily_mean)) + geom_point()+ stat_poly_line() + stat_poly_eq() 
```

```{r, fig.width=10, fig.height=5}
ggplot(data=fit.daily, aes(x=ER_mean, y=K600_daily_mean)) + geom_point()+ stat_poly_line() + stat_poly_eq() 

```


For Bayesian models only, you can dig even deeper using `get_mcmc`, which
returns a `stanfit` object that can be inspected using the `rstan` package.
(These traceplots are pretty bad because we used so few MCMC iterations. You
should strive for better in your final models.)
```{r, fig.width=10, fig.height=5}
mcmc <- get_mcmc(mm.test.frch)
rstan::traceplot(mcmc, pars='K600_daily', nrow=3)
```

```{r, fig.width=10, fig.height=5}
mcmc <- get_mcmc(mm.test.frch)
rstan::traceplot(mcmc, pars='GPP_daily', nrow=3)
```

```{r, fig.width=10, fig.height=5}
mcmc <- get_mcmc(mm.test.frch)
rstan::traceplot(mcmc, pars='ER_daily', nrow=3)
```

```{r, fig.width=10, fig.height=5}
fig3 <- plot_DO_preds(mm.test.frch)
```


``` {r}
frch.DO.pred <- predict_DO(mm.test.frch)

frch.DO.pred <- na.omit(frch.DO.pred)

lm(DO.obs~ DO.mod, data = frch.DO.pred)


frch.DO.pred$SM.date <- as.Date(frch.DO.pred$solar.time - 4*60*60)

frch.DO.pred$SM.date <- as.factor(frch.DO.pred$SM.date)


fit_model <- function(x, y) summary(lm(x ~ y))$adj.r.squared

# frch.DO.pred %>% 
#     group_nest(SM.date) %>% 
#     mutate(model = map(data, fit_model),

# day1 <- frch.DO.pred %>% filter(SM.date == "2019-07-16")
# summary(lm(DO.obs~DO.mod, data = day1))


test.run <- frch.DO.pred %>% group_by(SM.date) %>% summarise(adj.R2 = fit_model(DO.obs,DO.mod))

frch.DO.pred <- full_join(frch.DO.pred, test.run)



#DO.obs vs DO.mod
# oxy_preds<- lapply(fit.frch, predict_DO)


rsq <-  summary(lm(frch.DO.pred$DO.mod~frch.DO.pred$DO.obs))$r.squared

library(ggplot2)
p1 <- ggplot(frch.DO.pred, aes(x = solar.time)) + geom_point(aes(y=DO.obs, colour = "Observed DO"), color = "darkcyan") + geom_line(aes(y = DO.mod, colour= "Modeled DO"), color = "blue4") + theme(axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.title.x=element_blank() ) + labs(colour="Green", y = "DO (mg/L)") +  theme(legend.position="none") + ggtitle("Observed (points) and Modeled (lines)")

p2 <- ggplot(frch.DO.pred, aes(x = solar.time)) + geom_point(aes(y=adj.R2))
  
  # geom_line(aes(color = variable)) +
  #     facet_grid(variable ~ ., scales = "free_y") + theme(legend.position = "none")

library(grid)

grid.newpage()
grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), ggplotGrob(rhat)))

```

``` {r fig.width=8, fig.height=10}
grid.newpage()
grid.draw(rbind(ggplotGrob(p1), ggplotGrob(p2), ggplotGrob(rhat), ggplotGrob(gpp), ggplotGrob(er)))

```

``` {r}


```